\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{../thm}
\title{CS348 Assignment 2 Design}

\begin{document}

\maketitle

Generally, my coding style is that everything are executed in ``chains" -- a starting function calling one after another.
Also, the ``difficult" logic is done in SQL, i.e. sorting, so my program is about constructing a collection and then map each item to a specialized function.

\begin{itemize}
\item
{\bf BibAuthor}
How my {\tt BibAuthor} works is very simple. 
\begin{enumerate}
\item
{\bf Generate a sorted collection for looping} First, it calls {\tt print\_pubid()} to generate the sorted list of {\tt pubid}, {\tt name}, and {\tt year}.
Notice only the {\tt pubid} is used, and the rest are for sorting.

The query works by selecting 3 sets: from books, articles, and publications that are refered by the articles.
\item
{\bf Iterate through each pubid} Then, the program calls {\tt print\_pub\_by\_id} to iterate through each {\tt pubid} while remain in order.
This step identify type of the publication {\bf again} individual (second pass).
The query is similar to the first one, except it does left joins on each child table (book, article, journal, proceedings) and then determine the type by picking non-null values -- this works because these table are mutually exclusive.
\item
{\bf Query again for detail of publication} The rest is just matching the publication type, and then query the {\tt pubid} with the type's specialized function (i.e. {\tt print\_*\_details}).
This is the third pass.
The queries consists only simple selects -- nothing exciting.
\end{enumerate}
\item
{\bf BibMaint}
My BibMaint is also very simple.
The main point (and hope) is that everything runs in one transaction, so that I don't need to worry about update inconsistencies.

Notice that the insert/update processes for the publication table is the same for all articles, journals, proceedings, and books.
Similarly, the wrote table codes are shared between book and articles.

There are 3 types of insert/update:
\begin{itemize}
\item
{\bf Straight insert/update}: the author table -- it is just a simple insert/update statement.
\item
{\bf Publication}: whether a publication exists or not, {\tt process\_publication} will delete all details related to a {\tt pubid} (i.e. wrote, article, journal, proceedings, book).
\item
{\bf Insert the details}: the command determines which of {\tt process\_*} the program will be called upon, and the insert/update the database from parsed data.
\end{itemize}
\end{itemize}

\end{document}
